\section{Stimuli}

% The referenced figure was moved to the related work section to make it render on page 3 properly

Participants in our study were shown two scenes: a temple and a mountainous landscape. Example screenshots are shown in Fig.~\ref{fig:temple1}. These specific scenes were chosen in order to represent broad VR applications. The temple scene consists of primarily near focal distances, with three separate rooms with different illuminations: bright, natural and dark. All three rooms had high detail objects that a user could pay close attention to at close range. The mountainous landscape in contrast, consists of primarily far focal distances with few high detail objects. 
%Both are modified from freely available Unreal Engine demos. 
\\

A total of 16 participants took part, with an age range of 18 to 25 years old. Three participants were female and the rest were male. Participants interacted with the two scenes using a control scheme proposed by Valve software~\cite{valveVR}: the view vector of the Oculus is independent to the motion vector of the user's virtual avatar. The user controls the movement of their avatar using the keyboard to move forwards or backwards, or strafe left and right, and they use the mouse to rotate their avatar's torso.  Based on recommendations from~\cite{oculus}, jumping is disabled, and the user is limited to a velocity of $1.4ms^{-1}$, to minimise discomfort arising from factors related to traversing the virtual environment. Similarly, if a user's velocity has a non-zero vertical component (such as when they walk up stairs), their horizontal velocity is decreased to compensate, keeping their total velocity constant.\\
% Mention that this is done to reduce the discomfort impact of vertical motion

Participants were given minimal direction in what they were to do in the virtual scene: they were simply instructed to explore. This was done instead of specifying a track to follow as we wanted participants to move around these environments naturally. Participants were allowed to withdraw from the experiment at any time if they felt too sick.\\
